\textbf{Selective DNA and Protein Isolation from Marine Macrophyte Surfaces}

### 2020-02-04 submission/manuscript.Rmd
Silva datatbase switch to 138.

### Sequence Analysis
```{r}
# Calculation of the error rate based on the ATCC MSA-1002 mock community
error <- read_tsv("data/mothur/raw.trim.contigs.good.unique.good.filter.unique.precluster.pick.pick.pick.error.summary", na="") %>%
  filter(numparents==1) %>%
  mutate(mismatches_weight=weight*mismatches) %>%
  mutate(total_weight=weight*total)
error <- sum(error$mismatches_weight)/sum(error$total_weight)*100
# Calculation of the number of sequences in the negative control
nc <- read_tsv("data/mothur/raw.trim.contigs.good.unique.good.filter.unique.precluster.pick.nr_v132.wang.tax.summary") %>%
  filter(taxon=="Root") %>%
  select(NC_1)
```
Obtained sequences were analyzed on the computer cluster Isabella (University Computing Center, University of Zagreb) using mothur (version 1.43.0) [@Schloss2009] according to the MiSeq Standard Operating Procedure (MiSeq SOP; https://mothur.org/wiki/MiSeq_SOP) [@Kozich2013] and recommendations given from the Riffomonas project to enhance data reproducibility (http://www.riffomonas.org/). For alignment and classification of sequences the SILVA SSU Ref NR 99 database (release 132; http://www.arb-silva.de) was used [@Quast2013; @Yilmaz2014]. Sequences classified as chloroplasts by mothur were exported, aligned using SILVA incremental aligner (SINA, version 1.6.0) [@Pruesse2012] against the same SILVA SSU Ref NR 99 database (release 132) and imported into ARB (version 6.0.6) [@Ludwig2004] for further phylogenetic analysis using the same database. Reference sequences close to imported ones were selected and used to calculate a phylogenetic tree using the Maximum Likelihood algorithm RAxML (version 7.0.3) with 1000 tree replicates [@Stamatakis2006]. Imported partial chloroplast sequences were added to the tree using the maximum parsimony criteria and not allowing changes to tree topology. Pipeline data processing and visualization was done using R (version 3.6.0) [@RCoreTeam2019], package tidyverse (version 1.2.1) [@Wickham2019] and multiple other packages [@Xie2014; @Xie2015; @Xie2019a; @Xie2019; @Zhu2019; @Allaire2019; @Xie2018]. The detailed analysis procedure including the R Markdown file for this paper are available as a GitHub repository (**TO BE ADDED LATER!**). Based on the ATCC MSA-1002 mock community included in the analysis a sequencing error rate of `r error` \si{\percent} was determined, which is in line with previously reported values for next-generation sequencing data [@Kozich2013; @Schloss2016]. In addition, the negative control processed together with the samples yielded only `r nc` sequences after sequence quality curation.

>>>>

### Sequence Analysis
```{r}
# Calculation of the error rate based on the ATCC MSA-1002 mock community
error <- read_tsv("data/mothur/raw.trim.contigs.good.unique.good.filter.unique.precluster.pick.pick.pick.error.summary", na="") %>%
  filter(numparents==1) %>%
  mutate(mismatches_weight=weight*mismatches) %>%
  mutate(total_weight=weight*total)
error <- sum(error$mismatches_weight)/sum(error$total_weight)*100
# Calculation of the number of sequences in the negative control
nc <- read_tsv("data/mothur/raw.trim.contigs.good.unique.good.filter.unique.precluster.pick.nr_v138.wang.tax.summary") %>%
  filter(taxon=="Root") %>%
  select(NC_1)
```
Obtained sequences were analyzed on the computer cluster Isabella (University Computing Center, University of Zagreb) using mothur (version 1.43.0) [@Schloss2009] according to the MiSeq Standard Operating Procedure (MiSeq SOP; https://mothur.org/wiki/MiSeq_SOP) [@Kozich2013] and recommendations given from the Riffomonas project to enhance data reproducibility (http://www.riffomonas.org/). For alignment and classification of sequences the SILVA SSU Ref NR 99 database (release 138; http://www.arb-silva.de) was used [@Quast2013; @Yilmaz2014]. Sequences classified as chloroplasts by mothur were exported, aligned using SILVA incremental aligner (SINA, version 1.6.0) [@Pruesse2012] against the same SILVA SSU Ref NR 99 database (release 138) and imported into ARB (version 6.0.6) [@Ludwig2004] for further phylogenetic analysis using the same database. Reference sequences close to imported ones were selected and used to calculate a phylogenetic tree using the Maximum Likelihood algorithm RAxML (version 7.0.3) with 1000 tree replicates [@Stamatakis2006]. Imported partial chloroplast sequences were added to the tree using the maximum parsimony criteria and not allowing changes to tree topology. Pipeline data processing and visualization was done using R (version 3.6.0) [@RCoreTeam2019], package tidyverse (version 1.2.1) [@Wickham2019] and multiple other packages [@Xie2014; @Xie2015; @Xie2019a; @Xie2019; @Zhu2019; @Allaire2019; @Xie2018]. The detailed analysis procedure including the R Markdown file for this paper are available as a GitHub repository (**TO BE ADDED LATER!**). Based on the ATCC MSA-1002 mock community included in the analysis a sequencing error rate of `r error` \si{\percent} was determined, which is in line with previously reported values for next-generation sequencing data [@Kozich2013; @Schloss2016]. In addition, the negative control processed together with the samples yielded only `r nc` sequences after sequence quality curation.

### 2020-02-04 submission/manuscript.tex
Silva datatbase switch to 138.

Obtained sequences were analyzed on the computer cluster Isabella
(University Computing Center, University of Zagreb) using mothur
(version 1.43.0) (Schloss \emph{et al.}, 2009) according to the MiSeq
Standard Operating Procedure (MiSeq SOP;
\url{https://mothur.org/wiki/MiSeq_SOP}) (Kozich \emph{et al.}, 2013)
and recommendations given from the Riffomonas project to enhance data
reproducibility (\url{http://www.riffomonas.org/}). For alignment and
classification of sequences the SILVA SSU Ref NR 99 database (release
132; \url{http://www.arb-silva.de}) was used (Quast \emph{et al.}, 2013;
Yilmaz \emph{et al.}, 2014). Sequences classified as chloroplasts by
mothur were exported, aligned using SILVA incremental aligner (SINA,
version 1.6.0) (Pruesse \emph{et al.}, 2012) against the same SILVA SSU
Ref NR 99 database (release 132) and imported into ARB (version 6.0.6)
(Ludwig \emph{et al.}, 2004) for further phylogenetic analysis using the
same database. Reference sequences close to imported ones were selected
and used to calculate a phylogenetic tree using the Maximum Likelihood
algorithm RAxML (version 7.0.3) with 1000 tree replicates (Stamatakis,
2006). Imported partial chloroplast sequences were added to the tree
using the maximum parsimony criteria and not allowing changes to tree
topology. Pipeline data processing and visualization was done using R
(version 3.6.0) (R Core Team, 2019), package tidyverse (version 1.2.1)
(Wickham \emph{et al.}, 2019) and multiple other packages (Xie, 2014,
2015, 2019a, 2019b; Xie \emph{et al.}, 2018; Zhu, 2019; Allaire \emph{et
al.}, 2019). The detailed analysis procedure including the R Markdown
file for this paper are available as a GitHub repository (\textbf{TO BE
ADDED LATER!}). Based on the ATCC MSA-1002 mock community included in
the analysis a sequencing error rate of 0.009 \si{\percent} was
determined, which is in line with previously reported values for
next-generation sequencing data (Kozich \emph{et al.}, 2013; Schloss
\emph{et al.}, 2016). In addition, the negative control processed
together with the samples yielded only 2 sequences after sequence
quality curation.

@@

Isolated proteins were whole trypsin digested using the FASP
(filter-aided sample preparation) Protein Digestion Kit (Expedeon, UK)
according to the manufacturer's instructions (Wiśniewski \emph{et al.},
2009) with small modifications. Before loading the solution to the
column, protein pellets were solubilized in a urea sample buffer
included in the kit amended with DTT (final concentration 100
\si{\milli\Molar}) for 45 \si{\minute} at room temperature and
centrifuged at 20,000 × g for 2 -- 5 \si{\minute} at room temperature to
remove larger particles. The first washing step after protein solution
loading was repeated twice. In addition, centrifugation steps were
prolonged if the column was clogged. Trypsin digestion was performed on
column filters at 37 \si{\degreeCelsius} overnight for 18 \si{\hour}.
The final filtrate containing digested proteins was acidified with 1
\si{\percent} (final concentration) trifluoroacetic acid, freezed at
\num{-80} \si{\degreeCelsius} for 15 \si{\minute}, lyophilized and sent
to the Vienna Metabolomics Center (University of Vienna) for
metaproteomic analysis. \textbf{TO BE ADDED-VIENNA PART}.

@@

@@

\begin{figure}[h]

@@

\caption{Taxonomic classification and relative contribution of the most abundant bacterial sequences on the surfaces of two marine macrophytes (\textit{Cymodocea nodosa} and \textit{Caulerpa cylindracea}) from two locations (Saline and Funtana) and in two contrasting seasons (4 December 2017 and 19 June 2018).\label{community}}\label{fig:unnamed-chunk-2}
\end{figure}

>>>>

Obtained sequences were analyzed on the computer cluster Isabella
(University Computing Center, University of Zagreb) using mothur
(version 1.43.0) (Schloss \emph{et al.}, 2009) according to the MiSeq
Standard Operating Procedure (MiSeq SOP;
\url{https://mothur.org/wiki/MiSeq_SOP}) (Kozich \emph{et al.}, 2013)
and recommendations given from the Riffomonas project to enhance data
reproducibility (\url{http://www.riffomonas.org/}). For alignment and
classification of sequences the SILVA SSU Ref NR 99 database (release
138; \url{http://www.arb-silva.de}) was used (Quast \emph{et al.}, 2013;
Yilmaz \emph{et al.}, 2014). Sequences classified as chloroplasts by
mothur were exported, aligned using SILVA incremental aligner (SINA,
version 1.6.0) (Pruesse \emph{et al.}, 2012) against the same SILVA SSU
Ref NR 99 database (release 138) and imported into ARB (version 6.0.6)
(Ludwig \emph{et al.}, 2004) for further phylogenetic analysis using the
same database. Reference sequences close to imported ones were selected
and used to calculate a phylogenetic tree using the Maximum Likelihood
algorithm RAxML (version 7.0.3) with 1000 tree replicates (Stamatakis,
2006). Imported partial chloroplast sequences were added to the tree
using the maximum parsimony criteria and not allowing changes to tree
topology. Pipeline data processing and visualization was done using R
(version 3.6.0) (R Core Team, 2019), package tidyverse (version 1.2.1)
(Wickham \emph{et al.}, 2019) and multiple other packages (Xie, 2014,
2015, 2019a, 2019b; Xie \emph{et al.}, 2018; Zhu, 2019; Allaire \emph{et
al.}, 2019). The detailed analysis procedure including the R Markdown
file for this paper are available as a GitHub repository (\textbf{TO BE
ADDED LATER!}). Based on the ATCC MSA-1002 mock community included in
the analysis a sequencing error rate of 0.009 \si{\percent} was
determined, which is in line with previously reported values for
next-generation sequencing data (Kozich \emph{et al.}, 2013; Schloss
\emph{et al.}, 2016). In addition, the negative control processed
together with the samples yielded only 2 sequences after sequence
quality curation.

@@

Isolated proteins were whole trypsin digested using the FASP
(filter-aided sample preparation) Protein Digestion Kit (Expedeon, UK)
according to the manufacturer's instructions (Wiśniewski \emph{et al.},
2009) with small modifications. Before loading the solution to the
column, protein pellets were solubilized in a urea sample buffer
included in the kit amended with DTT (final concentration 100
\si{\milli\Molar}) for 45 \si{\minute} at room temperature and
centrifuged at 20,000 × g for 2 -- 5 \si{\minute} at room temperature to
remove larger particles. The first washing step after protein solution
loading was repeated twice. In addition, centrifugation steps were
prolonged if the column was clogged. Trypsin digestion was performed on
column filters at 37 \si{\degreeCelsius} overnight for 18 \si{\hour}.
The final filtrate containing digested proteins was acidified with 1
\si{\percent} (final concentration) trifluoroacetic acid, freezed at
\num{-80} \si{\degreeCelsius} for 15 \si{\minute}, lyophilized and sent
to the Vienna Metabolomics Center (University of Vienna) for
metaproteomic analysis. Peptides were resuspended in 1 \si{\percent}
(final concentration) trifluoroacetic acid, desalted using the Pierce
C18 Tips (Thermo Fisher Scientific, USA) according to the manufacturer's
instructions and sequenced on a Q Exactive Hybrid Quadrupole-Orbitrap
Mass Spectrometer (Thermo Fisher Scientific, USA). Obtained MS/MS
spectra were searched against a protein database from metagenomic
assembly published in Burke \emph{et al.} (2011a) using SEQUEST-HIT
engines and validated with Percolator in Proteome Discoverer 2.1 (Thermo
Fisher Scientific, USA). The target-decoy approach was used to reduce
the probability of false peptide identification. Results whose false
discovery rate at the peptide level was \SI{< 1}{\percent} were kept.
For protein identification a minimum of of two peptides and one unique
peptide were required. For protein quantification, a chromatographic
peak area-based free quantitative method was applied.

@@

\newpage 
\setlength\parindent{0pt}

\textbf{\autoref{micro_dec}.} \nameref{micro_dec}

\textbf{\autoref{micro_jun}.} \nameref{micro_jun}

\textbf{\autoref{community}.} \nameref{community}

@@

\begin{figure}[ht]

{\centering \includegraphics[width=0.85\linewidth]{../results/images/confocal_december}

\caption{Confocal microscope images of \textit{Cymodocea nodosa} and \textit{Caulerpa cylindracea} surfaces from different locations (Saline, Funtana-Invaded and Funtana-Noninvaded) sampled on 4 December 2017 and stained with SYBR Green I. Scale bar in all images is 60 \si{\um}.\label{micro_dec}}\label{fig:unnamed-chunk-2}
\end{figure}
\newpage
\begin{figure}[ht]

{\centering \includegraphics[width=0.85\linewidth]{../results/images/confocal_june}

\caption{Confocal microscope images of \textit{Cymodocea nodosa} and \textit{Caulerpa cylindracea} surfaces from different locations (Funtana-Invaded and Funtana-Noninvaded) sampled on 19 June 2018 and stained with SYBR Green I. Scale bar in all images is 60 \si{\um}.\label{micro_jun}}\label{fig:unnamed-chunk-3}
\end{figure}
\newpage
\begin{figure}[ht]

@@

\caption{Taxonomic classification and relative contribution of the most abundant bacterial sequences from surfaces of two marine macrophytes (\textit{Cymodocea nodosa} and \textit{Caulerpa cylindracea}) sampled in different locations (Saline, Funtana-Invaded and Funtana-Noninvaded) and in two contrasting seasons (4 December 2017 and 19 June 2018).\label{community}}\label{fig:unnamed-chunk-4}
\end{figure}
